Appendix 4: Model Comparison Code For Manuscript

### 2025-11-20 modelcomparison_code.Rmd
header formatting

##data cleaning

@@

## exploratory demographics table

```{r}
#library(gtsummary)
#library(dplyr)
#library(kableExtra)

#edata_clean <- data %>%
  #filter(de01 == 'man' | de01 == "woman") %>%
  #rename(
    #Gender = de01,
    #Age = de02,
    #DonationEligibility = bd01,
    #DonationCount = bd02,
    #DonationCountLast2years = bd03,
    #WeeksFromLastDonation = bd04
  #)

# Create summary table
#etable1 <- tbl_summary(
  #data = edata_clean,
  #include = c(Age, DonationEligibility, WeeksFromLastDonation, DonationCount, DonationCountLast2years),
  #by = Gender,
  #statistic = list(
    #all_continuous() ~ "{mean} ({sd})",   # Use mean (SD) for continuous vars
    #all_categorical() ~ "{n} ({p}%)"
  #)
#) %>%
  #add_n()  # Adds total N for each group

# Output as LaTeX
#as_kable_extra(etable1, format = "latex")

@@

@@

# a) Sum score model with robust estimator and listwise deletion

@@

#  b) Sum score model with bootstrapping and listwise deletion

@@

#  c) Sum score model with robust estimator and fiml

@@

#  d) Sum score model with bootstrapping and fiml

@@

# e) Latent factor model with robust estimator and listwise deletion

@@

# f) Latent factor model with boostrapping and listwise deletion

>>>>

## Data cleaning

@@

@@

## Missing data

@@

### a) Sum score model with robust estimator and listwise deletion

@@

###  b) Sum score model with bootstrapping and listwise deletion

@@

###  c) Sum score model with robust estimator and fiml

@@

###  d) Sum score model with bootstrapping and fiml

@@

### e) Latent factor model with robust estimator and listwise deletion

@@

### f) Latent factor model with boostrapping and listwise deletion
